\bf DOGE Days on Reddit: Decoding Public Sentiment in a Federal Shakeup

### 2025-03-21 code/paper.qmd
final paper draft

---
title: "DOGE Days on Reddit: Decoding Public Sentiment in a Federal Shakeup"
format:
  jasa-pdf:
    keep-tex: true  
    journal:
      blinded: false
  jasa-html: default
date: last-modified
author:
  - name: Kevin Linares
    affiliations:
      - name: University of Maryland
  - name: Felix Baez-Santiago
  - name: Aria Lu
  - name: Gloria Zhou
    affiliations:
      - name: University of Michigan
abstract: |
  This study explores the impact of the Department of Government Efficiency (DOGE)'s federal workforce reductions on public sentiment, utilizing Reddit as a data source. By scraping and analyzing posts and comments related to DOGE, we examined public reactions, including fear, anxiety, and support, during a period of significant governmental change. The analysis reveals how specific news events influenced online discourse and highlights the utility of social media for understanding public perception of policy impacts.
keywords:
  - Reddit
  - Federal Government
  - DOGE
editor: 
  markdown: 
    wrap: sentence
---

@@

# path to repo
repo_path <- str_c("~/Desktop/UMICH/SURV622_Assignment/data/") # felix
# repo_path <- str_c("~/repos/SURV622_Assignment/data/") # kevin

@@

Since it's inception in January of 2025, the Department of Government Efficiency (DOGE) has fired over 200,000 federal workers in an effort by the new administration to keep a campaign promise in reducing federal government.
However, DOGE's overreaching approach and often illegal tactics has resulted sparked fear and anxiety among the federal workforce, thus taking a toll on their mental health.
Many are uncertain about their career faith as it is in the hands of outsiders that disregard internal policies with no remorse.
The current topic on how DOGE is impacting federal worker's perceptions of job security is likely to continue and worsen over the next few months, given DOGE's nontransparent and unconventional methods without accountability.
We propose that Reddit as a platform offers researchers a vantage look into lively discussions, timely reactions, and grievances from federal workers on this topic.
Furthermore, we also expect to capture positive reactions to DOGE's approach in reducing the federal workforce.

@@

*Search Terms*.
Our preliminary Reddit API scrape allowed us to decide on a set of keyword searches related to this topic of research.
This was an iterative process that resulted in the use of 8 keywords we used to search for posts related to the topic of interest (see Table 1).
We excluded keywords that were either vague or broad such as "Elon Musk" or "drain the swamp." Additionally, we examined subreddit posts and found a plethora of unrelated posts using our keyword search list.
For instance, searching for "Fork in the Road" brought back several subreddits on motorcycles and mountain biking.
Additionally, searching for "DOGE" also brought back posts on DOGEcoin which is unrelated to our topic.
Therefore, we meticoulsly combed through a list of subreddits we acquired from our initial scrape and selected those that contaiend relevant posts.
To compensate for balance on this topic, we included conservative subreddits such as "neoliberal", "AskConservitives" as well as we avoided specific agency subreddits, for instance "NIH" or "CDC" as to not overwhelm one particular view point.
Overall we ended with 19 subreddits (see appendix) and 8 keywords resulting in 152 unique combinations to scrape.

@@

*Analytic Plan*.
We listened to the Reddit API from March 2 through the 10th on every top of the hour by scraping each combination of our seven keywords and 20 subreddits resulting in 152 API hits per hour.
Reddit API scraping limits were managed by setting a sleep timer in between API hits.
As new Reddit posts were scraped they were entered into a data table without preprocessing.
After the listening period, the accumulated number of unprocessed posts was 643.
Every row in our data table equated to one post, and we had 8 columns to include the date and time of the post, title and text of post, subreddit where the post derived from, number of comments associated with it, url, and we recorded the search term that was used to collect the post.
We processed the posts to exclude duplicates, and in some instance two different keywords resulted in scraping the same posts so we kept we dropped one of them.
Post text were cleaned in terms of removing weblinks and when possible translating special character such as the at sign to the word "at." The date column was converted to a date class variable and we extracted the day of the week and time of day from it to use in analysis.
Cleaning our scraped posts resulted in 557 posts.

A glance at the posts revealed that many of them are factual statements, questions, or re-postings of news articles and videos.
Therefore, these texts do not lend themselves to be coded for favorability, and we decided to also scrape the comments associated with each post.
This resulted in 12,553 comments, post processing, containing information about the score, up/down votes, and date/time posted.
We removed comments that had only a weblink, video, or image as these cannot be coded.
A look into some of these comments revealed more opinionated statements and reactions which we than randomly (without replacement) selected 400 comments assigned to four graduate students to code for whether the comment favored DOGE's approach to the reduction in the federal force, opposed, or was neutral.

@@

We show the number of posts pre/post processing by day in Figure 1 during the timeframe that we collected these data..
There appears to be a noticeable peak in activity during the middle of the week.
However, we don't have enough data across weeks to conclusively say it's due to the day of the week itself.
It's more likely that these spikes are linked to specific events that occurred on those days, which sparked conversations.
The two peaks in our graph could be attributed to two major news stories.
On March 5, Elon Musk made a statement about wanting to "save Western civilization from empathy," and on March 6, there were reports that President Trump was limiting Musk's authority due to backlash over cuts to DOGE.
These events likely had a significant impact on the volume of Reddit posts related to Elon Musk and DOGE, driving the observed spikes in activity.

On May third, news outlets started reporting that DOGE was claiming \$105 billion dollars in savings from cutting "wasteful" spending by layoffs and cutting foreign aid.
This amount is controversial since since the receipts shown on their site only amount to less than [\$9.6 billion](https://abcnews.go.com/US/doge-website-now-saved-105-billion-backtracked-earlier/story?id=119408347).
This could have prompted Reddit users to take to subreddits and provide their opinion or thoughts on this matter.

@@

We see a peak in the comments in Figure 2 during March 6th, which was a Thursday, and perhaps in anticipation of DOGE policies that often are released on Friday morning and have come to be known as "[Musk-acre Friday](https://smotus.substack.com/p/friday-night-musk-acre)."

@@

Most posts occur during the early morning, noon, and afternoon hours (see Figure 3).
The highest peak is around lunchtime, likely due to people posting during their lunch break.
There is also significant activity in the afternoon, evening, and early morning.
This could be because people have more free time or stay up late, allowing them to take the time to write posts, which require more effort than quick interactions.
The fewest posts are seen in the morning, which makes sense as people are typically getting ready for work, commuting, or sleeping in.
The trend for comments (see Figure 3) mirrors that of posts.
This makes sense because people are likely using Reddit at similar times for both posting and commenting.
However, the volume of comments is much higher than the number of posts, as each post receives many comments from different users.

@@

The graphs below (Figure 4) show the most frequent words used in both Reddit posts and their comment sections. These words were identified by tokenizing the text and removing stop words, then counting the occurrences of the most common terms. From the visualizations, we can see that many of these words are directly related to our topic of discussion. Specifically, there are frequent mentions of 'President,' 'DOGE,' 'federal government,' and 'RIF,' which suggest that discussions surrounding political events, cryptocurrency (like Dogecoin), and government-related issues are significant in the posts and comments. This highlights the focus of the community on these key themes, reflecting the ongoing conversations and interests of Reddit users within this context.

```{r}
# Tokenize words and count frequencies for Reddit posts
posts_word_counts <- posts_data_clean |>
  select(title, text) |>
  pivot_longer(cols = c(title, text), values_drop_na = TRUE) |>
  unnest_tokens(word, value) |>
  anti_join(stop_words, by = "word") |>
  count(word, sort = TRUE) |>
  slice_max(n, n = 25)

# Tokenize words and count frequencies for Reddit comments
comments_word_counts <- comments_data_clean |>
  select(comment) |>
  pivot_longer(cols = c(comment), values_drop_na = TRUE) |>
  unnest_tokens(word, value) |>
  anti_join(stop_words, by = "word") |>
  count(word, sort = TRUE) |>
  slice_max(order_by = n, n = 25)

@@

We randomly selected and coded 400 comments from the Reddit posts. The table below shows the distribution of favorability coding for these comments. Among the 400 comments, the majority (217) expressed opposition to DOGE's approach to reducing the federal workforce, while 110 were supportive, and 73 remained neutral. A large number of comments (12,153) were not coded, as their content was not relevant for favorability assessment.

@@

In this study, we explored the impact of the Department of Government Efficiency’s (DOGE) actions on federal workers’ perceptions of job security, using Reddit as a platform to analyze public discourse. By examining Reddit posts and comments related to DOGE’s workforce reduction policies, we gained valuable insights into the sentiments of both federal workers and the broader public. Our findings indicate that these discussions are heavily influenced by political events and high-profile figures, such as President Trump and Elon Musk, with particular attention given to DOGE’s controversial cost-cutting measures. Through the analysis of both posts and comments, we captured a wide range of reactions, with the majority being strongly opposed to DOGE’s approach. The frequent mention of terms like ‘President,’ ‘DOGE,’ ‘federal government,’ and ‘RIF’ underscores the community’s focus on government policies and the emotional responses these issues generate.

In terms of favorability, the distribution of comments revealed that 217 out of 400 were opposed to DOGE’s approach, 110 were supportive, and 73 were neutral. Additionally, patterns in post volume, especially peaks during significant news events, highlight the dynamic nature of these discussions, providing insights into the timing and public reactions to key policy decisions. While our study provides a snapshot of Reddit discussions during a specific period, the findings demonstrate the value of social media platforms like Reddit in capturing public sentiment on contemporary political and policy issues. However, it’s important to note that Reddit may not fully represent the broader population’s views, as the platform tends to skew younger and more politically engaged, potentially limiting the generalizability of these findings.

Furthermore, the use of sentiment analysis on social media presents challenges, as it can be influenced by sarcasm, humor, or polarized language, which might affect the accuracy of sentiment classification. The specific subreddits analyzed, while designed to capture diverse perspectives, may still over-represent certain political or ideological viewpoints. Additionally, the relatively short timeframe of this analysis—spanning only March 2-10, 2025—means that we may not have captured long-term trends or shifts in sentiment as the DOGE policies unfold. Future research could address these limitations by expanding the data collection to other platforms or a longer timeframe and by incorporating demographic data to better understand the views of different Reddit user groups.

@@

>>>>

---
title: "DOGE Days on Reddit: Decoding Public Sentiment in a Federal Shakeup"
format:
  jasa-pdf:
    keep-tex: true  
    journal:
      blinded: false
  jasa-html: default
date: last-modified
author:
  - name: Kevin Linares
    affiliations:
      - name: University of Maryland
  - name: Felix Baez-Santiago
  - name: Aria Lu
  - name: Gloria Zhou
    affiliations:
      - name: University of Michigan
abstract: |
  This study explores the impact of the Department of Government Efficiency (DOGE)'s federal workforce reductions, known as reduction in force (RIF), on public sentiment, utilizing Reddit as a data source. We scraped the Reddit API from March 2nd to March 10th resulting in 557 unique posts with 12,553 comments from subreddits related to DOGE's approach to the RIF. Our exploratory analysis captures peaks in the number of posts/comments following major news event coverage related to the RIF, highlighting the utility of social media for understanding public perception of policy impacts. Our text analysis reveals a saliency on community with words such as people, employees, service, public, workers, and care being top words in both posts and comments. Moreover, a team of researchers coded a random subset of comments for public sentiment and found that only a quarter approved of DOGE's actions towards the RIF.

keywords:
  - Reddit
  - Federal Government
  - DOGE
editor: 
  markdown: 
    wrap: sentence
---

@@

# path to repo
#repo_path <- str_c("~/Desktop/UMICH/SURV622_Assignment/data/") # felix
repo_path <- str_c("~/repos/SURV622_Assignment/data/") # kevin

@@

Since its inception in January 2025, the Department of Government Efficiency (DOGE) has implemented significant reductions in the federal workforce, resulting in the separation of over 200,000 employees, in alignment with the new administration's campaign promises.
These reductions have generated widespread concern and anxiety among federal workers regarding their job security and mental well-being.
Reports indicate that DOGE's methods have raised questions about adherence to established internal policies.
The ongoing debate surrounding DOGE's impact on federal worker perceptions of job security necessitates a thorough examination.
This study proposes that Reddit, as a platform for public discourse, provides researchers with valuable insights into real-time reactions and discussions among federal workers on this topic.
Furthermore, this research aims to capture a range of public sentiments, including both critical and supportive perspectives, regarding DOGE's workforce reduction efforts.

@@

*Search Terms*.
Our initial Reddit API scrape facilitated the development of a targeted keyword search strategy for this research.
This iterative process resulted in the selection of eight keywords (see Table 1).
We excluded keywords deemed vague or overly broad, such as 'Elon Musk' or 'drain the swamp.' Additionally, we observed that certain keywords yielded a high volume of irrelevant posts.
For example, 'policy changes' returned numerous discussions unrelated to government workforce reductions.
Similarly, 'DOGE' produced results related to DOGEcoin, which is outside the scope of this study.
Therefore, we meticulously examined the subreddits identified in our initial scrape and selected those containing relevant discussions.
To ensure a balanced representation of viewpoints, we included subreddits with conservative perspectives, such as 'neoliberal' and 'AskConservatives,' while avoiding subreddits focused on specific agencies like 'NIH' or 'CDC,' which could skew the data.
In total, we selected 19 subreddits (see Appendix A) and utilized eight keywords, resulting in 152 unique keyword and subreddit combinations for our data collection.

@@

*Analytic Plan*.
We collected data from the Reddit API hourly, from March 2nd through the 10th, by scraping each combination of our eight keywords and 19 subreddits, resulting in 152 API requests per hour.
Reddit API rate limits were managed by implementing a sleep timer between requests.
Raw data from new Reddit posts were entered into a data table without initial processing.
Following the data collection period, the raw dataset contained 643 posts.
Each row in the data table represented a single post, and the columns included the post's date and time, title, text, subreddit, comment count, URL, and the search term used for collection.
Duplicate posts, which occurred when multiple keywords matched the same post, were removed.
Post text was cleaned by removing weblinks and converting special characters, such as the at sign, to the word 'at.' The date column was converted to a date class variable, and the day of the week and time of day were extracted for analysis.
After cleaning, the dataset consisted of 557 posts.

A preliminary review of the posts revealed that many were factual statements, questions, or reposted news articles and videos, which were not suitable for sentiment coding.
Therefore, we also scraped the comments associated with each post.
This resulted in 12,553 comments after processing, including information on score, up/down votes, and date/time.
Comments containing only weblinks, videos, or images were removed.
A review of the comments revealed more opinionated statements and reactions.
We then randomly selected 400 comments (without replacement) and assigned them to four graduate students for coding, categorizing each comment as favoring, opposing, or neutral towards DOGE's approach to federal workforce reductions.

@@

We show the number of posts pre/post processing by day in Figure 1 during the timeframe that we collected these data.
There appears to be a noticeable peak in activity during the middle of the week.
However, we don't have enough data across weeks to conclusively say it is due to the day of the week itself.
It is more likely that these spikes are linked to specific events that occurred on those days, which sparked conversations.
The two peaks in our graph could be attributed to two major news stories.
On March 5th, Elon Musk made a statement about wanting to "save Western civilization from empathy," and on March 6th, there were reports that President Trump was limiting Musk's authority due to backlash over cuts to DOGE.
These events likely had a significant impact on the volume of Reddit posts related to Elon Musk and DOGE, driving the observed spikes in activity.

On March 3rd, news outlets started reporting that DOGE was claiming \$105 billion dollars in savings from cutting "wasteful" spending by layoffs and cutting foreign aid.
This amount is controversial since since the receipts shown on their site only amount to less than [\$9.6 billion](https://abcnews.go.com/US/doge-website-now-saved-105-billion-backtracked-earlier/story?id=119408347).
This could have prompted Reddit users to take to subreddits and provide their opinion or thoughts on this matter.

@@

We see a peak in the comments in Figure 2 on March 6th, which was a Thursday, and perhaps in anticipation of DOGE policies that often are released on Friday morning and have come to be known as "[Musk-acre Friday](https://smotus.substack.com/p/friday-night-musk-acre)."

@@

Most posts occur during the early morning, noon, and afternoon hours (see Figure 3).
The highest peak is around lunchtime, likely due to people posting during their lunch break.
There is also significant activity in the afternoon, evening, and early morning.
It is possible that people have more time in the evenings allowing them to be more likely to post on Reddit.
The fewest posts are seen in the morning, which makes sense as people are typically getting ready for work, commuting, or sleeping in.
The trend for comments (see Figure 3) mirrors that of posts.
This makes sense because people are likely using Reddit at similar times for both posting and commenting.
However, the volume of comments is much higher than the number of posts, as each post receives many comments from different users.

@@

The graphs below (Figure 4) show the most frequent words used in both Reddit posts and their comment sections while excluding our keyword search terms.
These words were identified by tokenizing the text and removing stop words, then counting the occurrences of the most common terms.
Examining this visual reveals that in posts the current president's name is the top word.
However, in both posts and comments, there appears to be an emerging theme of community as words like people, employees, service, care, jobs, and public are also top words.
This highlights the focus of the community on these key themes, reflecting the ongoing conversations and interests of Reddit users within this context.

```{r}
#| fig-width: 6
#| fig-height: 6
#| 
keywords <- posts_data_clean |>
    select( search_term) |>
    pivot_longer(cols = search_term, values_drop_na = TRUE) |>
    unnest_tokens(word, value) |> 
  distinct(word) |> 
  pull()

# Tokenize words and count frequencies for Reddit posts
posts_word_counts <- posts_data_clean |>
  select( text) |>
  pivot_longer(cols = text, values_drop_na = TRUE) |>
  unnest_tokens(word, value) |>
  anti_join(stop_words, by = "word") |>
  count(word, sort = TRUE) |>
  # remove keywords
  filter(!(word %in% keywords),
         # filter out numbers
         !str_detect(word, "[:digit:]") ) |> 
  slice_max(n, n = 30)

# Tokenize words and count frequencies for Reddit comments
comments_word_counts <- comments_data_clean |>
  select(comment) |>
  pivot_longer(cols = comment, values_drop_na = TRUE) |>
  unnest_tokens(word, value) |>
  anti_join(stop_words, by = "word") |>
  count(word, sort = TRUE) |>
  # remove keywords
  filter(!(word %in% keywords),
         # filter out numbers
         !str_detect(word, "[:digit:]") ) |> 
  slice_max(order_by = n, n = 30)

@@

We randomly selected and coded 400 comments from the Reddit posts.
Table 2 shows the distribution of favorability coding for these comments.
Among the 400 comments, the majority (217) expressed opposition to DOGE's approach to reducing the federal workforce, while 110 were supportive, and 73 remained neutral.
A large number of comments (12,153) were not coded, as their content was not relevant for favorability assessment.

@@

In this study, we explored the impact of the DOGE's actions towards the reduction in force impacting federal workers’ perceptions of job security, using Reddit as a platform to analyze public discourse.
In examining Reddit posts and comments related to DOGE’s workforce reduction policies, we gained valuable insights into the sentiments of both federal workers and the broader public.
Our findings indicate that these discussions are heavily influenced by political events and high-profile figures, such as President Trump and Elon Musk, with particular attention given to DOGE’s controversial cost-cutting measures.
Through the analysis of both posts and comments, we captured a wide range of reactions, with the majority being strongly opposed to DOGE’s approach.
The frequent mention of terms related to the administration underscores the community’s focus on government policies and the emotional responses these issues generate.

In terms of favorability, the distribution of comments revealed that 217 out of 400 were opposed to DOGE’s approach, 110 were supportive, and 73 were neutral.
Additionally, patterns in post volume, especially peaks during significant news events, highlight the dynamic nature of these discussions, providing insights into the timing and public reactions to key policy decisions.
While our study provides a snapshot of Reddit discussions during a specific period, the findings demonstrate the value of social media platforms like Reddit in capturing public sentiment on contemporary political and policy issues.
However, it is important to note that Reddit may not fully represent the broader population’s views, as the platform tends to skew younger and more politically engaged, potentially limiting the generalizability of these findings.

The use of sentiment analysis on social media presents challenges, as it can be influenced by sarcasm, humor, or polarized language, which might affect the accuracy of sentiment classification.
Therefore, our research team hand coded a subset of comments, yet inter-rater reliability was not estimated.
The specific subreddits analyzed, while designed to capture diverse perspectives, may still over-represent certain political or ideological viewpoints.
Moreover, the relatively short timeframe of this analysis—spanning only March 2nd to March 10th—means that we may not have captured long-term trends or shifts in sentiment as the DOGE policies unfold.
Future research could address these limitations by expanding the data collection to other platforms or a longer timeframe and by incorporating demographic data to better understand the views of different Reddit user groups.

@@

We examined almost 100 subreddit posts while paying attention to the post topics and determined which ones were related to our topic.
We also included right leaning subreddits to attempt to capture a balanced public sentiment on the topic.
The following is our final list of subreddits that we scraped from.

### 2025-03-21 code/paper.tex
final paper draft

\date{March 20, 2025}
\title{\bf DOGE Days on Reddit: Decoding Public Sentiment in a Federal
Shakeup}
\author{
Kevin Linares\\
University of Maryland\\
and\\Felix Baez-Santiago\\
and\\Aria Lu\\
and\\Gloria Zhou\\
University of Michigan\\
}
\maketitle

\bigskip
\bigskip
\begin{abstract}
This study explores the impact of the Department of Government
Efficiency (DOGE)'s federal workforce reductions on public sentiment,
utilizing Reddit as a data source. By scraping and analyzing posts and
comments related to DOGE, we examined public reactions, including fear,
anxiety, and support, during a period of significant governmental
change. The analysis reveals how specific news events influenced online
discourse and highlights the utility of social media for understanding
public perception of policy impacts.
\end{abstract}

@@

\emph{Search Terms}. Our preliminary Reddit API scrape allowed us to
decide on a set of keyword searches related to this topic of research.
This was an iterative process that resulted in the use of 8 keywords we
used to search for posts related to the topic of interest (see Table 1).
We excluded keywords that were either vague or broad such as ``Elon
Musk'' or ``drain the swamp.'' Additionally, we examined subreddit posts
and found a plethora of unrelated posts using our keyword search list.
For instance, searching for ``Fork in the Road'' brought back several
subreddits on motorcycles and mountain biking. Additionally, searching
for ``DOGE'' also brought back posts on DOGEcoin which is unrelated to
our topic. Therefore, we meticoulsly combed through a list of subreddits
we acquired from our initial scrape and selected those that contaiend
relevant posts. To compensate for balance on this topic, we included
conservative subreddits such as ``neoliberal'', ``AskConservitives'' as
well as we avoided specific agency subreddits, for instance ``NIH'' or
``CDC'' as to not overwhelm one particular view point. Overall we ended
with 19 subreddits (see appendix) and 8 keywords resulting in 152 unique
combinations to scrape.

@@

\emph{Analytic Plan}. We listened to the Reddit API from March 2 through
the 10th on every top of the hour by scraping each combination of our
seven keywords and 20 subreddits resulting in 152 API hits per hour.
Reddit API scraping limits were managed by setting a sleep timer in
between API hits. As new Reddit posts were scraped they were entered
into a data table without preprocessing. After the listening period, the
accumulated number of unprocessed posts was 643. Every row in our data
table equated to one post, and we had 8 columns to include the date and
time of the post, title and text of post, subreddit where the post
derived from, number of comments associated with it, url, and we
recorded the search term that was used to collect the post. We processed
the posts to exclude duplicates, and in some instance two different
keywords resulted in scraping the same posts so we kept we dropped one
of them. Post text were cleaned in terms of removing weblinks and when
possible translating special character such as the at sign to the word
``at.'' The date column was converted to a date class variable and we
extracted the day of the week and time of day from it to use in
analysis. Cleaning our scraped posts resulted in 557 posts.

A glance at the posts revealed that many of them are factual statements,
questions, or re-postings of news articles and videos. Therefore, these
texts do not lend themselves to be coded for favorability, and we
decided to also scrape the comments associated with each post. This
resulted in 12,553 comments, post processing, containing information
about the score, up/down votes, and date/time posted. We removed
comments that had only a weblink, video, or image as these cannot be
coded. A look into some of these comments revealed more opinionated
statements and reactions which we than randomly (without replacement)
selected 400 comments assigned to four graduate students to code for
whether the comment favored DOGE's approach to the reduction in the
federal force, opposed, or was neutral.

@@

We show the number of posts pre/post processing by day in Figure 1
during the timeframe that we collected these data.. There appears to be
a noticeable peak in activity during the middle of the week. However, we
don't have enough data across weeks to conclusively say it's due to the
day of the week itself. It's more likely that these spikes are linked to
specific events that occurred on those days, which sparked
conversations. The two peaks in our graph could be attributed to two
major news stories. On March 5, Elon Musk made a statement about wanting
to ``save Western civilization from empathy,'' and on March 6, there
were reports that President Trump was limiting Musk's authority due to
backlash over cuts to DOGE. These events likely had a significant impact
on the volume of Reddit posts related to Elon Musk and DOGE, driving the
observed spikes in activity.

On May third, news outlets started reporting that DOGE was claiming
\$105 billion dollars in savings from cutting ``wasteful'' spending by
layoffs and cutting foreign aid. This amount is controversial since
since the receipts shown on their site only amount to less than
\href{https://abcnews.go.com/US/doge-website-now-saved-105-billion-backtracked-earlier/story?id=119408347}{\$9.6
billion}. This could have prompted Reddit users to take to subreddits
and provide their opinion or thoughts on this matter.

@@

We see a peak in the comments in Figure 2 during March 6th, which was a
Thursday, and perhaps in anticipation of DOGE policies that often are
released on Friday morning and have come to be known as
``\href{https://smotus.substack.com/p/friday-night-musk-acre}{Musk-acre
Friday}.''

@@

The graphs below (Figure 4) show the most frequent words used in both
Reddit posts and their comment sections. These words were identified by
tokenizing the text and removing stop words, then counting the
occurrences of the most common terms. From the visualizations, we can
see that many of these words are directly related to our topic of
discussion. Specifically, there are frequent mentions of `President,'
`DOGE,' `federal government,' and `RIF,' which suggest that discussions
surrounding political events, cryptocurrency (like Dogecoin), and
government-related issues are significant in the posts and comments.
This highlights the focus of the community on these key themes,
reflecting the ongoing conversations and interests of Reddit users
within this context.

@@

In this study, we explored the impact of the Department of Government
Efficiency's (DOGE) actions on federal workers' perceptions of job
security, using Reddit as a platform to analyze public discourse. By
examining Reddit posts and comments related to DOGE's workforce
reduction policies, we gained valuable insights into the sentiments of
both federal workers and the broader public. Our findings indicate that
these discussions are heavily influenced by political events and
high-profile figures, such as President Trump and Elon Musk, with
particular attention given to DOGE's controversial cost-cutting
measures. Through the analysis of both posts and comments, we captured a
wide range of reactions, with the majority being strongly opposed to
DOGE's approach. The frequent mention of terms like `President,' `DOGE,'
`federal government,' and `RIF' underscores the community's focus on
government policies and the emotional responses these issues generate.

In terms of favorability, the distribution of comments revealed that 217
out of 400 were opposed to DOGE's approach, 110 were supportive, and 73
were neutral. Additionally, patterns in post volume, especially peaks
during significant news events, highlight the dynamic nature of these
discussions, providing insights into the timing and public reactions to
key policy decisions. While our study provides a snapshot of Reddit
discussions during a specific period, the findings demonstrate the value
of social media platforms like Reddit in capturing public sentiment on
contemporary political and policy issues. However, it's important to
note that Reddit may not fully represent the broader population's views,
as the platform tends to skew younger and more politically engaged,
potentially limiting the generalizability of these findings.

Furthermore, the use of sentiment analysis on social media presents
challenges, as it can be influenced by sarcasm, humor, or polarized
language, which might affect the accuracy of sentiment classification.
The specific subreddits analyzed, while designed to capture diverse
perspectives, may still over-represent certain political or ideological
viewpoints. Additionally, the relatively short timeframe of this
analysis---spanning only March 2-10, 2025---means that we may not have
captured long-term trends or shifts in sentiment as the DOGE policies
unfold. Future research could address these limitations by expanding the
data collection to other platforms or a longer timeframe and by
incorporating demographic data to better understand the views of
different Reddit user groups.

>>>>

\date{March 21, 2025}
\title{\bf DOGE Days on Reddit: Decoding Public Sentiment in a Federal
Shakeup}
\author{
Kevin Linares\\
University of Maryland\\
and\\Felix Baez-Santiago\\
and\\Aria Lu\\
and\\Gloria Zhou\\
University of Michigan\\
}
\maketitle

\bigskip
\bigskip
\begin{abstract}
This study explores the impact of the Department of Government
Efficiency (DOGE)'s federal workforce reductions, known as reduction in
force (RIF), on public sentiment, utilizing Reddit as a data source. We
scraped the Reddit API from March 2nd to March 10th resulting in 557
unique posts with 12,553 comments from subreddits related to DOGE's
approach to the RIF. Our exploratory analysis captures peaks in the
number of posts/comments following major news event coverage related to
the RIF, highlighting the utility of social media for understanding
public perception of policy impacts. Our text analysis reveals a
saliency on community with words such as people, employees, service,
public, workers, and care being top words in both posts and comments.
Moreover, a team of researchers coded a random subset of comments for
public sentiment and found that only a quarter approved of DOGE's
actions towards the RIF.
\end{abstract}

@@

\emph{Search Terms}. Our initial Reddit API scrape facilitated the
development of a targeted keyword search strategy for this research.
This iterative process resulted in the selection of eight keywords (see
Table 1). We excluded keywords deemed vague or overly broad, such as
`Elon Musk' or `drain the swamp.' Additionally, we observed that certain
keywords yielded a high volume of irrelevant posts. For example, `policy
changes' returned numerous discussions unrelated to government workforce
reductions. Similarly, `DOGE' produced results related to DOGEcoin,
which is outside the scope of this study. Therefore, we meticulously
examined the subreddits identified in our initial scrape and selected
those containing relevant discussions. To ensure a balanced
representation of viewpoints, we included subreddits with conservative
perspectives, such as `neoliberal' and `AskConservatives,' while
avoiding subreddits focused on specific agencies like `NIH' or `CDC,'
which could skew the data. In total, we selected 19 subreddits (see
Appendix A) and utilized eight keywords, resulting in 152 unique keyword
and subreddit combinations for our data collection.

@@

\emph{Analytic Plan}. We collected data from the Reddit API hourly, from
March 2nd through the 10th, by scraping each combination of our eight
keywords and 19 subreddits, resulting in 152 API requests per hour.
Reddit API rate limits were managed by implementing a sleep timer
between requests. Raw data from new Reddit posts were entered into a
data table without initial processing. Following the data collection
period, the raw dataset contained 643 posts. Each row in the data table
represented a single post, and the columns included the post's date and
time, title, text, subreddit, comment count, URL, and the search term
used for collection. Duplicate posts, which occurred when multiple
keywords matched the same post, were removed. Post text was cleaned by
removing weblinks and converting special characters, such as the at
sign, to the word `at.' The date column was converted to a date class
variable, and the day of the week and time of day were extracted for
analysis. After cleaning, the dataset consisted of 557 posts.

A preliminary review of the posts revealed that many were factual
statements, questions, or reposted news articles and videos, which were
not suitable for sentiment coding. Therefore, we also scraped the
comments associated with each post. This resulted in 12,553 comments
after processing, including information on score, up/down votes, and
date/time. Comments containing only weblinks, videos, or images were
removed. A review of the comments revealed more opinionated statements
and reactions. We then randomly selected 400 comments (without
replacement) and assigned them to four graduate students for coding,
categorizing each comment as favoring, opposing, or neutral towards
DOGE's approach to federal workforce reductions.

@@

We show the number of posts pre/post processing by day in Figure 1
during the timeframe that we collected these data. There appears to be a
noticeable peak in activity during the middle of the week. However, we
don't have enough data across weeks to conclusively say it is due to the
day of the week itself. It is more likely that these spikes are linked
to specific events that occurred on those days, which sparked
conversations. The two peaks in our graph could be attributed to two
major news stories. On March 5th, Elon Musk made a statement about
wanting to ``save Western civilization from empathy,'' and on March 6th,
there were reports that President Trump was limiting Musk's authority
due to backlash over cuts to DOGE. These events likely had a significant
impact on the volume of Reddit posts related to Elon Musk and DOGE,
driving the observed spikes in activity.

On March 3rd, news outlets started reporting that DOGE was claiming
\$105 billion dollars in savings from cutting ``wasteful'' spending by
layoffs and cutting foreign aid. This amount is controversial since
since the receipts shown on their site only amount to less than
\href{https://abcnews.go.com/US/doge-website-now-saved-105-billion-backtracked-earlier/story?id=119408347}{\$9.6
billion}. This could have prompted Reddit users to take to subreddits
and provide their opinion or thoughts on this matter.

@@

We see a peak in the comments in Figure 2 on March 6th, which was a
Thursday, and perhaps in anticipation of DOGE policies that often are
released on Friday morning and have come to be known as
``\href{https://smotus.substack.com/p/friday-night-musk-acre}{Musk-acre
Friday}.''

@@

The graphs below (Figure 4) show the most frequent words used in both
Reddit posts and their comment sections while excluding our keyword
search terms. These words were identified by tokenizing the text and
removing stop words, then counting the occurrences of the most common
terms. Examining this visual reveals that in posts the current
president's name is the top word. However, in both posts and comments,
there appears to be an emerging theme of community as words like people,
employees, service, care, jobs, and public are also top words. This
highlights the focus of the community on these key themes, reflecting
the ongoing conversations and interests of Reddit users within this
context.

@@

In this study, we explored the impact of the DOGE's actions towards the
reduction in force impacting federal workers' perceptions of job
security, using Reddit as a platform to analyze public discourse. In
examining Reddit posts and comments related to DOGE's workforce
reduction policies, we gained valuable insights into the sentiments of
both federal workers and the broader public. Our findings indicate that
these discussions are heavily influenced by political events and
high-profile figures, such as President Trump and Elon Musk, with
particular attention given to DOGE's controversial cost-cutting
measures. Through the analysis of both posts and comments, we captured a
wide range of reactions, with the majority being strongly opposed to
DOGE's approach. The frequent mention of terms related to the
administration underscores the community's focus on government policies
and the emotional responses these issues generate.

In terms of favorability, the distribution of comments revealed that 217
out of 400 were opposed to DOGE's approach, 110 were supportive, and 73
were neutral. Additionally, patterns in post volume, especially peaks
during significant news events, highlight the dynamic nature of these
discussions, providing insights into the timing and public reactions to
key policy decisions. While our study provides a snapshot of Reddit
discussions during a specific period, the findings demonstrate the value
of social media platforms like Reddit in capturing public sentiment on
contemporary political and policy issues. However, it is important to
note that Reddit may not fully represent the broader population's views,
as the platform tends to skew younger and more politically engaged,
potentially limiting the generalizability of these findings.

The use of sentiment analysis on social media presents challenges, as it
can be influenced by sarcasm, humor, or polarized language, which might
affect the accuracy of sentiment classification. Therefore, our research
team hand coded a subset of comments, yet inter-rater reliability was
not estimated. The specific subreddits analyzed, while designed to
capture diverse perspectives, may still over-represent certain political
or ideological viewpoints. Moreover, the relatively short timeframe of
this analysis---spanning only March 2nd to March 10th---means that we
may not have captured long-term trends or shifts in sentiment as the
DOGE policies unfold. Future research could address these limitations by
expanding the data collection to other platforms or a longer timeframe
and by incorporating demographic data to better understand the views of
different Reddit user groups.
